---
title: "Sample Code for Benjamini-Yekutieli Procedure"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
---
  
  ```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This R Markdown document contains sample code for performing simulation studies 
related to Benjamini-Yekutieli's method for control of the False Discovery Rate.


```{r}
library(tidyverse)
library(furrr)
library(cmstatr)
library(pwr)

plan(multisession, workers = 12)
```


In these simulation studies we consider the case of two groups, with the same
number of units of analysis in each group, and with the outcome vectors for the
units of analysis within a particular group being independently generated from a
single Multivariate Normal distribution. The mean vectors for the Multivariate
Normal distributions of the two groups differ. The two Multivariate Normal 
distributions will have the same covariance matrix in this setting. 
The outcomes for a single unit of analysis may have be correlated depending on 
the covariance matrix that is entered in the simulation study.

To summarize, if we let $\mathbf{y}_{i,j}$ denote the vector of $k$ outcomes for
unit $i = 1, \ldots, n$ in group $j = 1, 2$, then we assume that
$$\mathbf{y}_{i,j} \sim \mathrm{N}_k(\mathbf{\mu}_j, \mathbf{\Sigma})$$
independently.

```{r}

# Essential functions

generate_data = function(number_observations, mu_vector, covariance_matrix)
{
  chol_covariance_matrix = chol(covariance_matrix)
  
  random_normal = matrix(rnorm((number_observations*length(mu_vector))), 
                         ncol=number_observations, nrow=length(mu_vector))
  
  outcomes = t(chol_covariance_matrix)%*%random_normal + 
             matrix(rep(mu_vector, number_observations), 
                    ncol=number_observations, nrow=length(mu_vector))
  
  return(t(outcomes))
}

calculate_FWE_FDR_TDR = function(number_data_sets = 1e3,
                                 nominal_significance_level = 0.05,
                                 number_endpoints = 10,
                                 number_group_1 = 100, number_group_2 = 100, 
                                 mu_1 = rep(0, number_endpoints),
                                 mu_2 = rep(0, number_endpoints),
                                 sigma_vector = rep(1, number_endpoints), 
                                 rho = 0.5)
{
  # The number of outcomes is denoted by number_endpoints
  
  # The total number of observations across the two groups is denoted by 
  # total_number_observations
  
  # The number of observations in group 1 is number_group_1
  
  # The mu vectors for the two groups are denoted by mu_1 and mu_2, respectively
  
  # For simplicity, here we consider the case of being given a vector of 
  # standard deviations for the different outcomes (sigma_vector), 
  # and that the different outcomes have a constant correlation parameter (rho)
  
  # The entries for which the null hypothesis of the endpoints is "false" are 
  # denoted by active_endpoint_indicator
  
  active_endpoint_indicator = as.numeric(mu_1-mu_2!=0)
  
  false_rejections = rep(0, number_data_sets)
  FWER = rep(0, number_data_sets)
  FDR = rep(0, number_data_sets)
  TDR = rep(0, number_data_sets)
  
  covariance_matrix = diag(sigma_vector^2)
  for(i in 1:(number_endpoints-1))
  {
    for(j in (i+1):number_endpoints)
    {
      covariance_matrix[i,j] = rho*sigma_vector[i]*sigma_vector[j]
    }
  }
  
  covariance_matrix = t(covariance_matrix) + covariance_matrix - 
                      diag(sigma_vector^2)
  
  repeat_iterations = function(i)
  {
    new_group_1 = generate_data(number_group_1, mu_1, covariance_matrix)
    new_group_2 = generate_data(number_group_2, mu_2, covariance_matrix)
    
    test_statistics = as.vector(
      sapply((1:number_endpoints), 
              function(x){t.test(new_group_1[,x],new_group_2[,x],
                                 var.equal=TRUE)$statistic}))
    
    p_values = as.vector(
      sapply((1:number_endpoints), 
              function(x){t.test(new_group_1[,x],new_group_2[,x],
                                 var.equal=TRUE)$p.value}))
    
    endpoint_indicator = (1:number_endpoints)[order(p_values)]    
    active_endpoint_indicator = active_endpoint_indicator[order(p_values)]
    ordered_p_values = p_values[order(p_values)]
    BY_significance_levels = nominal_significance_level*
                             ((1:number_endpoints)/(number_endpoints*sum(1/(1:number_endpoints))))
    rejection_indicators = as.numeric(ordered_p_values<=
                                      BY_significance_levels)
    
    if(sum(rejection_indicators)==0)
    {
      false_rejections[i]<<-0
      FWER[i]<<-0
      FDR[i]<<-0
      TDR[i]<<-0
    }
    
    if(sum(rejection_indicators)>0)
    {
      if(length((1:length(rejection_indicators))[rejection_indicators==0])==0)
      {
        false_rejections[i]<<-number_endpoints-
                              sum(active_endpoint_indicator==1)
        FWER[i]<<-as.numeric(false_rejections[i]>0)
        FDR[i]<<-false_rejections[i]/sum(rejection_indicators)
        TDR[i]<<-sum(active_endpoint_indicator==1)/sum(rejection_indicators)
      }
      
      if(length((1:length(rejection_indicators))[rejection_indicators==0])>0)
      {
        first_failure_to_reject_indicator =
          min((1:length(rejection_indicators))[rejection_indicators==0])
        
        false_rejections[i]<<-sum(active_endpoint_indicator[1:(first_failure_to_reject_indicator-1)]==0)
        FWER[i]<<-as.numeric(false_rejections[i]>0)
        FDR[i]<<-false_rejections[i]/sum(rejection_indicators)
        TDR[i]<<-sum(active_endpoint_indicator[1:(first_failure_to_reject_indicator-1)]==1)/
                 sum(rejection_indicators)
      }
    }
  }
  
  #pb = txtProgressBar(min=1, max=number_data_sets, style=3, width=50, char="=")
    
  repeat_the_iterations = sapply(1:number_data_sets, 
                                 function(x)
                                 {
                                   repeat_iterations(x)
                                   #setTxtProgressBar(pb, x)
                                 })
  
  Type_I_FWE = sum(FWER)/number_data_sets
  mean_FDR = mean(FDR)
  mean_TDR = mean(TDR)
  
  return(c(Type_I_FWE, mean_FDR, mean_TDR))
}
```


Let's consider a collection of sample cases in which 2 out of 10 endpoints are active, and in which each group has $100$ units of analysis.

```{r}

number_data_sets = 1e3
number_endpoints = 10
number_group_1 = 100
number_group_2 = 100
mu_1 = rep(0, number_endpoints)
sigma_vector = rep(1, number_endpoints)
```

In the first set of cases, we have an effect size of $0.2$ and correlation parameters of $\rho = 0.2, 0.5, 0.8$. 

```{r}
mu_2 = c(0.2,0.2,rep(0, (number_endpoints-2)))

rho = 0.2

calculate_FWE_FDR_TDR (number_data_sets, nominal_significance_level = 0.05,
                       number_endpoints, number_group_1, number_group_2, 
                       mu_1, mu_2, sigma_vector, rho)

rho = 0.5

calculate_FWE_FDR_TDR (number_data_sets, nominal_significance_level = 0.05,
                       number_endpoints, number_group_1, number_group_2, 
                       mu_1, mu_2, sigma_vector, rho)

rho = 0.8

calculate_FWE_FDR_TDR (number_data_sets, nominal_significance_level = 0.05,
                       number_endpoints, number_group_1, number_group_2, 
                       mu_1, mu_2, sigma_vector, rho)
```


In the second set of cases, we have an effect size of $0.5$ and correlation parameters of $\rho = 0.2, 0.5, 0.8$. 

```{r}
mu_2 = c(0.5,0.5,rep(0, (number_endpoints-2)))

rho = 0.2

calculate_FWE_FDR_TDR (number_data_sets, nominal_significance_level = 0.05,
                       number_endpoints, number_group_1, number_group_2, 
                       mu_1, mu_2, sigma_vector, rho)

rho = 0.5

calculate_FWE_FDR_TDR (number_data_sets, nominal_significance_level = 0.05,
                       number_endpoints, number_group_1, number_group_2, 
                       mu_1, mu_2, sigma_vector, rho)

rho = 0.8

calculate_FWE_FDR_TDR (number_data_sets, nominal_significance_level = 0.05,
                       number_endpoints, number_group_1, number_group_2, 
                       mu_1, mu_2, sigma_vector, rho)
```


In the third set of cases in this setting, we have an effect size of $1$ and correlation parameters of $\rho = 0.2, 0.5, 0.8$. 

```{r}
mu_2 = c(1,1,rep(0, (number_endpoints-2)))

rho = 0.2

calculate_FWE_FDR_TDR (number_data_sets, nominal_significance_level = 0.05,
                       number_endpoints, number_group_1, number_group_2, 
                       mu_1, mu_2, sigma_vector, rho)

rho = 0.5

calculate_FWE_FDR_TDR (number_data_sets, nominal_significance_level = 0.05,
                       number_endpoints, number_group_1, number_group_2, 
                       mu_1, mu_2, sigma_vector, rho)

rho = 0.8

calculate_FWE_FDR_TDR (number_data_sets, nominal_significance_level = 0.05,
                       number_endpoints, number_group_1, number_group_2, 
                       mu_1, mu_2, sigma_vector, rho)
```


We now consider a collection of sample cases in which 5 out of 10 endpoints are active, and in which each group has $100$ units of analysis.

```{r}

number_data_sets = 1e3
number_endpoints = 10
number_group_1 = 100
number_group_2 = 100
mu_1 = rep(0, number_endpoints)
sigma_vector = rep(1, number_endpoints)
```

In the first set of cases, we have an effect size of $0.2$ and correlation parameters of $\rho = 0.2, 0.5, 0.8$. 

```{r}
mu_2 = c(rep(0.2,5),rep(0,(number_endpoints-5)))

rho = 0.2

calculate_FWE_FDR_TDR (number_data_sets, nominal_significance_level = 0.05,
                       number_endpoints, number_group_1, number_group_2, 
                       mu_1, mu_2, sigma_vector, rho)

rho = 0.5

calculate_FWE_FDR_TDR (number_data_sets, nominal_significance_level = 0.05,
                       number_endpoints, number_group_1, number_group_2, 
                       mu_1, mu_2, sigma_vector, rho)

rho = 0.8

calculate_FWE_FDR_TDR (number_data_sets, nominal_significance_level = 0.05,
                       number_endpoints, number_group_1, number_group_2, 
                       mu_1, mu_2, sigma_vector, rho)
```


In the second set of cases, we have an effect size of $0.5$ and correlation parameters of $\rho = 0.2, 0.5, 0.8$. 

```{r}
mu_2 = c(rep(0.5,5),rep(0,(number_endpoints-5)))

rho = 0.2

calculate_FWE_FDR_TDR (number_data_sets, nominal_significance_level = 0.05,
                       number_endpoints, number_group_1, number_group_2, 
                       mu_1, mu_2, sigma_vector, rho)

rho = 0.5

calculate_FWE_FDR_TDR (number_data_sets, nominal_significance_level = 0.05,
                       number_endpoints, number_group_1, number_group_2, 
                       mu_1, mu_2, sigma_vector, rho)

rho = 0.8

calculate_FWE_FDR_TDR (number_data_sets, nominal_significance_level = 0.05,
                       number_endpoints, number_group_1, number_group_2, 
                       mu_1, mu_2, sigma_vector, rho)
```


In the third set of cases in this setting, we have an effect size of $1$ and correlation parameters of $\rho = 0.2, 0.5, 0.8$. 

```{r}
mu_2 = c(rep(1,5),rep(0,(number_endpoints-5)))

rho = 0.2

calculate_FWE_FDR_TDR (number_data_sets, nominal_significance_level = 0.05,
                       number_endpoints, number_group_1, number_group_2, 
                       mu_1, mu_2, sigma_vector, rho)

rho = 0.5

calculate_FWE_FDR_TDR (number_data_sets, nominal_significance_level = 0.05,
                       number_endpoints, number_group_1, number_group_2, 
                       mu_1, mu_2, sigma_vector, rho)

rho = 0.8

calculate_FWE_FDR_TDR (number_data_sets, nominal_significance_level = 0.05,
                       number_endpoints, number_group_1, number_group_2, 
                       mu_1, mu_2, sigma_vector, rho)
```


We finally consider a collection of sample cases in which 8 out of 10 endpoints are active, and in which each group has $100$ units of analysis.

```{r}

number_data_sets = 1e3
number_endpoints = 10
number_group_1 = 100
number_group_2 = 100
mu_1 = rep(0, number_endpoints)
sigma_vector = rep(1, number_endpoints)
```

In the first set of cases, we have an effect size of $0.2$ and correlation parameters of $\rho = 0.2, 0.5, 0.8$. 

```{r}
mu_2 = c(rep(0.2,8),rep(0,(number_endpoints-8)))

rho = 0.2

calculate_FWE_FDR_TDR (number_data_sets, nominal_significance_level = 0.05,
                       number_endpoints, number_group_1, number_group_2, 
                       mu_1, mu_2, sigma_vector, rho)

rho = 0.5

calculate_FWE_FDR_TDR (number_data_sets, nominal_significance_level = 0.05,
                       number_endpoints, number_group_1, number_group_2, 
                       mu_1, mu_2, sigma_vector, rho)

rho = 0.8

calculate_FWE_FDR_TDR (number_data_sets, nominal_significance_level = 0.05,
                       number_endpoints, number_group_1, number_group_2, 
                       mu_1, mu_2, sigma_vector, rho)
```


In the second set of cases, we have an effect size of $0.5$ and correlation parameters of $\rho = 0.2, 0.5, 0.8$. 

```{r}
mu_2 = c(rep(0.5,8),rep(0,(number_endpoints-8)))

rho = 0.2

calculate_FWE_FDR_TDR (number_data_sets, nominal_significance_level = 0.05,
                       number_endpoints, number_group_1, number_group_2, 
                       mu_1, mu_2, sigma_vector, rho)

rho = 0.5

calculate_FWE_FDR_TDR (number_data_sets, nominal_significance_level = 0.05,
                       number_endpoints, number_group_1, number_group_2, 
                       mu_1, mu_2, sigma_vector, rho)

rho = 0.8

calculate_FWE_FDR_TDR (number_data_sets, nominal_significance_level = 0.05,
                       number_endpoints, number_group_1, number_group_2, 
                       mu_1, mu_2, sigma_vector, rho)
```


In the third set of cases in this setting, we have an effect size of $1$ and correlation parameters of $\rho = 0.2, 0.5, 0.8$. 

```{r}
mu_2 = c(rep(1,8),rep(0,(number_endpoints-8)))

rho = 0.2

calculate_FWE_FDR_TDR (number_data_sets, nominal_significance_level = 0.05,
                       number_endpoints, number_group_1, number_group_2, 
                       mu_1, mu_2, sigma_vector, rho)

rho = 0.5

calculate_FWE_FDR_TDR (number_data_sets, nominal_significance_level = 0.05,
                       number_endpoints, number_group_1, number_group_2, 
                       mu_1, mu_2, sigma_vector, rho)

rho = 0.8

calculate_FWE_FDR_TDR (number_data_sets, nominal_significance_level = 0.05,
                       number_endpoints, number_group_1, number_group_2, 
                       mu_1, mu_2, sigma_vector, rho)
```